Mobility Boomerang Plots

### 2020-07-23 notebooks/embedding_boomerang_plots.rmd
added points to 20 country plot, changed line color

plot <- df %>%
  filter(!is.na(`l2-norm`)) %>%
  filter(country %in% c(selected)) %>%
  ggplot(aes(x = size, y = `l2-norm`)) +
  stat_smooth(
    method = "loess",
    size = 2,
    se = T,
    level = 0.99,
    color = "black",
    fill = "black",
    alpha = 0.4,

>>>>

plot <- df %>%
  filter(!is.na(`l2-norm`)) %>%
  filter(country %in% c(selected)) %>%
  ggplot(aes(x = size, y = `l2-norm`)) +
  geom_point(alpha = 0.3) +
  stat_smooth(
    method = "loess",
    size = 1,
    se = T,
    level = 0.99,
    color = "#2980b9",
    fill = "#2980b9",
    alpha = 0.4,
